---
title: Scatterplot
author: Gabby
date: '2017-10-18'
slug: scatterplot
categories: []
tags: []
---

The scatter plot is the first data visualization that we will do. So, let's take the homeruns and strikeouts from the Lahman database and make a scatterplot. 

First, we will load our libraries. This will tell the computer what sets of data we are going to identify. 
```{r message=FALSE, warning=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
library(devtools)
```

Onto the next step! We are going to look at the career homeruns and strikeouts from players who had more than 400 homeruns. 
```{r message=FALSE, warning=FALSE}
#query<-"SELECT playerID,sum(HR),sum(SO)
#FROM Batting
#GROUP BY playerID
#HAVING sum(HR)>400"
#sqldf(query)

```

Now that we have the information, we will save it as a result. 

```{r message=FALSE, warning=FALSE}
query<-"SELECT playerID,sum(HR) AS Career_HR,sum(SO) As Career_SO 
FROM Batting GROUP BY playerID
HAVING sum(HR)>=400"
result<-sqldf(query)
#Now the data will turn into points by associating the homeruns with the y-axis and strikeouts with the x-axis. Also, we will add the graph title and the axis labels. 
ggplot()+  
  geom_point(data=result,aes(x=Career_SO,y=Career_HR),size=3)+
  ggtitle("Career Strikeouts and Homeruns")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")
```

YAY!! Now you know how to make a scatter plot! 