---
title: 'Scatter Plots '
author: ''
date: '2017-10-10'
slug: scatter-plots
categories: []
tags: [scatterplot,data visualization]
---
The scatter plot is the first data visualization that we will do. So, let's take the homeruns and strikeouts from the Lahman database and make a scatterplot. 

First, we will load our libraries. This will tell the computer what sets of data we are going to identify. 
```{r}
library(Lahman)
library(sqldf)
library(ggplot2)

```

Onto the next step! We are going to look at the career homeruns and strikeouts from players who had more than 400 homeruns. 
```{r}
query<-"SELECT playerID,sum(HR),sum(SO)
FROM Batting
GROUP BY playerID
HAVING sum(HR)>400"
sqldf(query)

```

Now that we have the information, we will save it as a result. 

```{r}
query<-"SELECT playerID,sum(HR) AS CareerHR,sum(SO) As CareerSO 
FROM Batting
HAVING sum(HR)>400"
result<-sqldf(query)
```

Now the data will turn into points by associating the homeruns with the y-axis and strikeouts with the x-axis. Also, we will add the graph title and the axis labels. 

```{r}
ggplot()+  
  geom_point(data=result,aes(x=CareerSO,y=CareerHR),size=3)+
  ggtitle("Career Strikeouts and Homeruns")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")
```

YAY!! Now you know how to make a scatter plot! 