---
title: Bar Plot
author: Gabby
date: '2017-10-18'
slug: bar-plot
categories: []
tags: []
---

This is our last data visualization that we will be doing! We are going to work on the bar plots. 

```{r message=FALSE,warning=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
library(devtools)
```

With a bar plot, we will look at the team homerun totals for all the MLB teams in 1980. 

```{r message=FALSE,warning=FALSE}
query<-"SELECT name,HR FROM Teams
WHERE yearID=1980
ORDER BY HR"
result<-sqldf(query)

result$name<-factor(result$name,levels=result$name)
```

The last time listed above is saving this information as a factor.  This will give assistance of how the order of the results appear in the order we stated. 

```{r message=FALSE,warning=FALSE}
ggplot()+
  geom_bar(data=result,aes(x=name,y=HR),stat='identity')+
  coord_flip()+
  ggtitle("1980 Team Homerun Totals")+
  xlab("Team Name")+
  ylab("Homeruns")
```

And that is it!! You learned all the data visualizations throught the ggplot2.  